The Effects of the 2023 Rule Changes in Major League Baseball

### 2023-11-10 manuscript/paper.tex
added boxplots code to code folder, included it in manuscript with description

%% preamble: Keep it clean; only include those you need
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}

@@

@@

To visually compare 2023 baseball statistics versus those in 2022, two histograms
were created for each variable with 2023's data overlaid on 2022's. Figure~\ref{fig:Fig2}
illustrates an example of this for the Stolen Bases variable, as we think this
metric may be most affected by the rule changes, as stated previously. Both
histograms exhibit fairly similar distributions; however, in 2023, there is a
noticeable increase in the number of players with 20 or more stolen bases. This
observation supports our intuition that the rule changes contributed to an uptick
in this variable.

@@

>>>>

%% preamble:
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{setspace}

@@

\doublespacing

@@

To visually compare 2023 baseball statistics versus those in 2022, two histograms
were created for each variable with 2023's data overlaid on 2022's. Figure~\ref{fig:Fig2}
illustrates an example of this for the Stolen Bases variable, as we think this
metric may be most affected by the rule changes, as stated previously. Both
histograms exhibit fairly similar distributions; however, in 2023, there is a
noticeable increase in the number of players with 20 or more stolen bases. This
observation supports our intuition that the rule changes contributed to an uptick
in this variable. Side by side boxplots for 2022 versus 2023 were also created for
each variable as shown in Figure~\ref{fig:Fig3}. The Stolen Bases statistic again
sticks out, having a greater median and more high outliers in 2023. Expected Batting Average (XBA)
and Slugging Percentage (SLG Percent) both look intriguing as well. As said above
with Game Length, the statistical significance of the difference in these statistics
from 2022 to 2023 will be tested in Section~\ref{sec:meth}.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics{boxplots}
  \caption{Matrix of boxplots illustrating the evolution of baseball statistics
  from 2022 to 2023, encompassing strikeout rates, walk rates, batting averages,
  slugging percentages, BABIP, total stolen bases, GIDP, ground ball hits, and xBA.}
  \label{fig:Fig3}
\end{figure}
